---
title: "p8105_hw1_vd2392"
author: "Vihar Desu"
output: html_document
---
### Imports
```{r}
library(tidyverse)
library(ggplot2)
```

### Problem 1: Constructing Data Frame
```{r dataframe}
df <- tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0,
  character_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = c("low", "low", "low", "med", "med", "med", "high", "high", "high", "high")
)
```

### Problem 1: Taking Means
Prompt: Try to take the mean of each variable in your data frame. What works and what doesn’t?
Answer: While the random normal vector and the boolean vector return numerical values, the character and factor vector throw errors.
```{r means}
mean(pull(df, samp)) #Works
mean(pull(df, samp_gt_0)) #Works
mean(pull(df, character_vec)) #Error: argument is not numeric or logical: returning NA[1] NA
mean(pull(df, factor_vec)) #Error: argument is not numeric or logical: returning NA[1] NA
```

### Problem 1: Typing Vectors
Prompt: Type the vectors to numeric values
Answer: The character and factor vectors can not be coerced conveniently. NAs are introduced by coercion. There is a type mismatch that does not work.
```{r typing}
as.numeric(pull(df, samp))
as.numeric(pull(df, samp_gt_0))
as.numeric(pull(df, character_vec))
as.numeric(pull(df, factor_vec))

```

### Problem 1: Multiplication
```{r multiplication}
samp_gt_0_asfactor <- as.factor(pull(df, samp_gt_0))
samp_gt_0_asnumeric <- as.numeric(pull(df, samp_gt_0))
samp_gt_0_asfactor * pull(df, samp)
samp_gt_0_asnumeric * pull(df, samp)
as.numeric(samp_gt_0_asfactor) * pull(df, samp)
```

### Problem 2: Penguins Dataset
The summary can be viewed below. 
There are 344 rows.
There are 8 columns.
The mean of flipper length = 200.9.

```{r penguins}
data("penguins", package = "palmerpenguins")
summary(penguins) #sisplays summary data
nrow(penguins) #344
ncol(penguins) #8
mean(pull(penguins, flipper_length_mm), na.rm=TRUE) #200.9
```

### Problem 2: Scatterplot
```{r scatterplot}
scatterplot <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species))
final_plot <- scatterplot + geom_point()
ggsave(device = "pdf", filename="scatterplot.pdf")
```



